Stability And Performance Of Virtual Aggregations Of Prosumers Through Diversification In The Smart Grid

### 2015-07-31 Article.tex
update

\begin{figure}
\includegraphics[scale=.6]{real_utility_2}
\caption{Utility of random coalitions depending on their size. Blue dots shows real mean utility values and the thick red curve its smoothed version by applying a Savitzky-Golay filter. On this plot the $ \alpha $ parameter of the utility function was selected according to equation \ref{eq:alpha_star} in order to favor 40 agents coalitions.}
\label{fig:real_utility2}
\end{figure}

@@

Figure \ref{fig:coalitions} shows the coalitions formed with the considered algorithms in the contract value / volatility space. The color map in the background indicates regions where we expect high utilities (red) and the ones where we expect very poor utility values (blue). The bottom right corner, with high contract values and low volatilities, is therefore the region where we wish to form our coalitions. A single coalition is represented by a marker, and the color and shape of a marker indicates by which algorithm the coalition has been formed. Besides, the sizes of the coalitions are indicated on the markers, and the marker size is also proportional to the coalition size. We can see that the utility function results in approximatively balanced coalitions. Small yellow markers indicates the gravity centers of their respective coalition structures. The coalitions of correlated agents (green squares) are clearly of poor quality according to our criteria since they can only afford small production contracts, and with a very high volatility.

>>>>

\begin{figure}
\includegraphics[scale=.6]{real_utility_2}
\caption{Utility of random coalitions depending on their size. Blue dots show real mean utility values and the thick red curve its smoothed version by applying a Savitzky-Golay filter. On this plot the $ \alpha $ parameter of the utility function was selected according to equation \ref{eq:alpha_star} in order to favor 40 agents coalitions.}
\label{fig:real_utility2}
\end{figure}

@@

Figure \ref{fig:coalitions} shows the coalitions formed with the considered algorithms in the contract value / volatility space. The color map in the background indicates regions where we expect high utilities (red) and the ones where we expect very poor utility values (blue). The bottom right corner, with high contract values and low volatilities, is therefore the region where we wish to form our coalitions. A single coalition is represented by a marker and the color and shape of a marker indicates by which algorithm the coalition has been formed. Besides, the sizes of the coalitions are indicated on the markers, and the marker size is also proportional to the coalition size. We can see that the utility function results in approximatively balanced coalitions. Small yellow markers indicates the gravity centers of their respective coalition structures. The coalitions of correlated agents (green squares) are clearly of poor quality according to our criteria since they can only afford small production contracts, and with a very high volatility.
